\textbf{Causal graph quantum dynamic simulation}

### 2021-06-02 paper/paper.tex
optimized some loops, made the code more readable, and optimized memory usage A LOT

Even including floating points errors, we can esaily do this test with around 5 steps, obtain around 200k graphs after the 5 forward iteration, and comme back to the same step within 0.001\% error in the magnitude.

@@

		// add right node
		nodes_.insert(nodes_.begin() + idx + 1,
			node_t(buff_idx, node, point_r_idx));

@@

\begin{lstlisting}[style=CStyle]
	//...
	void split_merge(std::vector<split_merge_t>& split_merge) {
		/* first check if there are any split or merges */

@@

		// check for last merge 
		/* ... */
		if (last_merge()) {
			name_->merge(last_idx);
			overflow_right(left_);
			split_merge.pop_back();
			/* ... */
		}

@@

		// split and merge names 
		// and calculating max displacement 
		int total_displacement = 0;
		for (auto split_merge_it = split_merge.rbegin(); split_merge_it != split_merge.rend(); ++split_merge_it)
			if ((*split_merge_it).second == split_t) {
				first_split |= name_->split((*split_merge_it).first) && (*split_merge_it).first == 0;

				++total_displacement;
			} else {
				name_->merge((*split_merge_it).first);
				--total_displacement;
			}

		// move particules 
		int displacement = total_displacement;
		auto split_merge_it = last_split_merge;
		for (auto left_it = left_.rbegin(); left_it != left_.rend(); ++left_it) {
			// check if there are any nodes left 
			while (split_merge_it >= split_merge.begin()) {
				// check if the node is split or merged 
				if ((*split_merge_it).first >= *left_it) {
					if ((*split_merge_it).second == split_t) {
						--displacement; // decrement the displacement 
					} else
						++displacement; // decrement the displacement 
					--split_merge_it;
				} else
					break;

			}

			if (split_merge_it == split_merge.begin() && displacement == 0)
				break;

			*left_it += displacement;
		}

		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 48 by a ">" */

@@

	/* first check if there are any particules to check */

@@

\begin{lstlisting}[style=CStyle]
\end{lstlisting}

@@

\begin{lstlisting}[style=CStyle]
\end{lstlisting}

>>>>

Even including floating points errors, we can esaily do this test with around 5 steps, obtain around 7M graphs after the 5 forward iteration, and comme back to the same step within $10^{-6}$ error in the magnitude.

@@

		// add right node
		nodes_.emplace(nodes_.begin() + idx + 1, buff_idx, node, point_r_idx);

@@

\begin{lstlisting}[style=CStyle]
	//...
	void split_merge(std::vector<split_merge_t>& split_merge) {
		if (split_merge.empty())
			return;

@@

		// check for last merge
		if (split_merge.back() == split_merge_t(size() - 1, merge_t)) {
			name_->merge(size() - 1);
			overflow_right(left_);	
			split_merge.pop_back();
		}

@@

		// and calculating max displacement 
		int total_displacement = 0;
		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
			if (type == split_t) {
				++total_displacement;
			} else
				--total_displacement;

		// reserve space for nodes
		name_->reserve(total_displacement);

		// split and merge names
		for (auto & [pos, type] : split_merge | std::ranges::views::reverse)
			if (type == split_t) {
				first_split |= name_->split(pos);
			} else
				name_->merge(pos);

		// move particules
		auto const split_merge_begin = split_merge.rend();
		int displacement = total_displacement;
		auto split_merge_it = split_merge.rbegin();
		for (auto &left_it : left_ | std::ranges::views::reverse) {
			// check if there are any nodes left
			for (;split_merge_it->first >= left_it && split_merge_it != split_merge_begin; ++split_merge_it)
				// check if the node is split or merged
				if (split_merge_it->second == split_t) {
						--displacement; // decrement the displacement 
					} else
						++displacement; // decrement the displacement

			//check if we can exit
			if (split_merge_it == split_merge_begin && displacement == 0)
				break;

			left_it += displacement;
		}

		/* we than do the exact same thing with particule going to the right, rplacing ">=" at line 42 by a ">" */

@@

@@

\begin{lstlisting}[style=CStyle]
	//...
	void reduce_all() {
		for(auto it = graphs_.begin(); it != graphs_.end();) {
			// range of similar graphs to delete
			auto upper = graphs_.equal_range(it->first).second;

			for(auto jt = std::next(it); jt != upper; ++jt)
		    	it->second += jt->second;

			// if the first graphgs has a zero probability, erase the whole range
			if (!check_zero(it->second))
				++it;

			it = graphs_.unsafe_erase(it, upper);
		}
	}
	//...
\end{lstlisting}

@@

\begin{lstlisting}[style=CStyle]
	//...
	void step_split_merge_all() {
		graph_map_t buff;
		buff.swap(graphs_);

		#pragma omp parallel
		#pragma omp single
		for (auto & [graph, mag] : buff)
		#pragma omp task
	  	{

	  		graph->step(); //not present for reversed_split_merge_step_all()

	  		auto split_merge = get_split_merge(graph);

	  		#pragma omp task
	  		{
	  			// update the probability of the graph without split or merge 
				auto [_, mag_no_split_merge] = subset(split_merge, 0, non_merge_, merge_);

				// copy and graph->reversed_step() befor insert for reversed_split_merge_step_all()
				graphs_.insert({graph, mag * mag_no_split_merge});
	  		}

	  		// add all graphs that actually have some split ot merge 
	  		const int n_max = num_subset(split_merge);
	  		for (int j = 1; j < n_max; ++j)
	  		#pragma omp task
	  		{
	  			graph_t* g_ = graph->copy();

	  			auto [split_merge_list, mag_split_merge] = subset(split_merge, j, non_merge_, merge_);

	  			// graph->reversed_step() befor insert for reversed_split_merge_step_all()
	  			g_->split_merge(split_merge_list);

	  			//add graph
	  			graphs_.insert({g_, mag * mag_split_merge});
	  		}
	  	}
	}
	//...
\end{lstlisting}
